Methods for Large Scale Learning to Rank

### 2014-04-07 report/Chapters/CrossBenchmarkComparison.tex
linear regression reference
method references geplaatst

AdaRank-\acs{MAP} & \cite{Xu2007} &  & Linear Regression &  & \cite{Wang2012, Volkovs2011} \\ 

@@

DCMP & \cite{Renjifo2012}  & \cite{Renjifo2012}  & RankBoost &  & \cite{Busa-Fekete2013} \\ 

@@

Energy\acs{nDCG} & \cite{Freno2011} & \cite{Freno2011} & RankDE &  & \cite{Sato2013} \\ 

@@

Focused\acs{SVM} & \cite{Niu2012} & \cite{Niu2012} & Rank\acs{RLS} &  &  \\ 

@@

GRank\acs{RLS} & \cite{Pahikkala2010} & \cite{Pahikkala2010} & Ridge Regression &  &  \\ 

@@

LAC-MR-OR & \cite{Veloso2008} & \cite{Veloso2008} & \acs{SVM}$^{\acs{MAP}}$ &  & \cite{Wang2012, Xu2008, Niu2012} \\ 
LambdaMART & \cite{Burges2010} & \cite{Asadi2013a, Ganjisaffar2011c} & SwarmRank &  & \cite{Sato2013} \\ 
LambdaNeuralRank & \cite{Papini2012} & \cite{Papini2012} & TGRank &  & \cite{Lai2013} \\ 

>>>>

AdaRank-\acs{MAP} & \cite{Xu2007} &  & Linear Regression & \cite{Cossock2006} & \cite{Wang2012, Volkovs2011} \\ 

@@

DCMP & \cite{Renjifo2012}  & \cite{Renjifo2012}  & RankBoost & \cite{Freund2003} & \cite{Busa-Fekete2013} \\ 

@@

Energy\acs{nDCG} & \cite{Freno2011} & \cite{Freno2011} & RankDE & \cite{Bollegala2011} & \cite{Sato2013} \\ 

@@

Focused\acs{SVM} & \cite{Niu2012} & \cite{Niu2012} & Rank\acs{RLS} & \cite{Pahikkala2009} & \cite{Pahikkala2010} \\ 

@@

GRank\acs{RLS} & \cite{Pahikkala2010} & \cite{Pahikkala2010} & Ridge Regression & \cite{Cossock2006} &  \\ 

@@

LAC-MR-OR & \cite{Veloso2008} & \cite{Veloso2008} & \acs{SVM}$^{\acs{MAP}}$ & \cite{Yue2007} & \cite{Wang2012, Xu2008, Niu2012} \\ 
LambdaMART & \cite{Burges2010} & \cite{Asadi2013a, Ganjisaffar2011c} & SwarmRank & \cite{Diaz-Aviles2009} & \cite{Sato2013} \\ 
LambdaNeuralRank & \cite{Papini2012} & \cite{Papini2012} & TGRank & \cite{Lai2013} & \cite{Lai2013} \\ 
